### 2019-05-30 CV/cv-sections/papers.tex
-

\cventry
{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik and Sebastian U. Stich} % Role
{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}}
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Samuel Horváth and Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov and Peter Richtárik} % Role
{Stochastic Spectral and Conjugate Descent Methods} % Title
{} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}}
\end{cvitems}
}

>>>>

\cventry
{Samuel Horváth, Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik, Sebastian U. Stich} % Role
{Stochastic Distributed Learning with Gradient Quantization and Variance Reduction} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1904.05115}{arXiv 2019}}
	\end{cvitems}
}

\cventry
{Dmitry Kovalev, Samuel Horváth, Peter Richtárik} % Role
{Don't Jump Through Hoops and Remove Those Loops: SVRG and Katyusha are Better Without the Outer Loop} % Title
{} % Location
{Jan. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1901.08689}{arXiv 2019}}
	\end{cvitems}
}

@@

\cventry
{Dmitry Kovalev, Eduard Gorbunov, Elnur Gasanov, Peter Richtárik} % Role
{Stochastic Spectral and Conjugate Descent Methods} % Title
{} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\href{https://papers.nips.cc/paper/7596-stochastic-spectral-and-conjugate-descent-methods}{NeurIPS 2018}}
\end{cvitems}
}
